---
title: "F2"
author: "Maxime Delmas"
date: "2023-02-27"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(PTXQC)
library(rjson)
library(effsize)
library(ggpubr)
library(grid)
```

## functions

```{r}

read_predictions <- function(path){
  json.str <- readLines(path, ok = T, warn = F)
  json.data <- fromJSON(json.str[1])
  return(json.data)
}

# From the json data, creates the data.frame, with columns: subject.id, preds.label, preds.probas, rank
extract_prediction_proba_pairs <- function(json.data){
  
  # Get length
  N <- length(json.data[["result"]])
  M <- length(json.data[["result"]][[1]][["preds"]])
  
  # inti the dataset
  dataset <- data.frame(subject.id = vector("character", N * M), preds.label = vector("character", N * M), preds.probas = vector("numeric", N * M), preds.rank = rep(c(1:M), N))
  
  for(i in 1:N) {
    
    # get the data and fill to the corresponding indexes.
    result <- json.data[["result"]][[i]]
    
    splited.uuid <- strsplit(result[["uuid"]], "-")[[1]]
    subject.id <- splited.uuid[1]
    
    # preds
    preds <- unlist(result[["preds"]])
    preds.label <- preds[seq(1, length(preds), 2)]
    preds.probas <- preds[seq(2, length(preds), 2)]
    
    is.correct <- rep(FALSE, M)
    if(length(result[["corrected_preds"]]) > 0) {
      # correct preds
      correct.preds <- unlist(result[["corrected_preds"]])
      correct.preds.label <- correct.preds[seq(1, length(correct.preds), 2)]
      correct.preds.rank <- as.numeric(correct.preds[seq(2, length(correct.preds), 2)])
      
      # test if preds in correct preds
      is.correct <- preds.label %in% correct.preds.label
    }
    
    dataset[(M*(i - 1) + 1):(M * i ), "subject.id"] <- subject.id
    dataset[(M*(i - 1) + 1):(M * i ), "preds.label"] <- preds.label
    dataset[(M*(i - 1) + 1):(M * i ), "preds.probas"] <- as.numeric(preds.probas)
    dataset[(M*(i - 1) + 1):(M * i ), "is.correct"] <- is.correct
    
  }
  return(dataset)
}



create_plot <- function(big.df, ref){

      sub.df <- big.df[big.df$ref == ref, ]
    data_for_plot <- sub.df %>% mutate(masked.rank.bin = cut(rank.in.masked, breaks = c(-1, 1, 2, 5, 10, 20, 50), labels = c('exclusive', "top1", "top [2-5[", "top [5-10[", "[10-20[", "[20-50["), include.lowest = T, right = F))
    data_for_plot <- data_for_plot %>% group_by(ref, preds.rank, masked.rank.bin) %>% summarise(n = n())
    data_for_plot <- data_for_plot %>% group_by(ref, preds.rank) %>% mutate(prop = (n/sum(n)) * 100)
    data_for_plot$masked.rank.bin <- factor(data_for_plot$masked.rank.bin, levels = c('exclusive', "top1", "top [2-5[", "top [5-10[", "[10-20[", "[20-50["))
    
    p <- data_for_plot %>% ggplot(aes(x = preds.rank, y = prop, fill = masked.rank.bin)) +
      geom_bar(stat="identity", width=1) +
      theme_classic() +
      scale_fill_discrete(drop=FALSE) +
      theme(axis.text = element_text(size = 20, , colour="black"), text = element_text(size = 15, colour="black")) +
      xlab("") + 
      ylab("")
      # ggtitle(paste("property= ", ref)) +
    return(p)

}



longest_common_prefix <- function(x, y) {
    # Remove punctation or digit characters (if chemical for instance):
    process_str <- function(x) {
      tolower(gsub('[[:punct:][:digit:]]+','',x))
    }
    x.processed <- process_str(x)
    y.processed <- sapply(y, FUN = process_str, simplify = T, USE.NAMES = F)
    
    longest <- 0
    # cut x by space
    for (ind.x in strsplit(x.processed, " ")[[1]]) {
      # print(ind.x)
      # also test on all y cuted by space
      for(ind.y in unlist(sapply(y.processed, FUN = function(x){strsplit(x, " ")}, simplify = T, USE.NAMES = F)) ){
        
        # test if longest prefix is
        l <- nchar(longestCommonPrefix(c(ind.x, ind.y)))
        
        if(l > longest){
          longest <- l
        }
      }
    }
    return(longest)
}

read_test_data <- function(path){
  
  lines <- readLines(path, ok = T, warn = F)
  
  N <- length(lines)
  
  out <- data.frame("subject.id" = vector("character", N), "subject.label" = vector("character", N), "object.labels" = vector("character", N), LCP = vector("numeric", N))

  for(index in 1:N){
    
    line <- lines[index]
    
    json.data <- fromJSON(line)
    
    subject.id <- json.data[["sub_uri"]]
    
    # On ne considère pas les synonymes car ils ne sont pas envoyé au modèle.
    subject.label <- json.data[["sub_label"]]
    
    object.labels <- c(json.data[["obj_labels"]], unlist(json.data[["obj_aliases"]])) #
    
    LCP <- longest_common_prefix(x = subject.label, object.labels)
    
    out[index, "subject.id"] <- subject.id
    out[index, "subject.label"] <- subject.label
    out[index, "object.labels"] <- paste(object.labels, collapse="; ")
    out[index, "LCP"] <- LCP
  }
  return(out)
}

frequency_of_object_in_train_data <- function(path){
  
  name_normalise <- function(name){
    
    # lower
    name <- tolower(name)
    
    # remove punctuation and space
    name <- gsub("[[:punct:]]", "", name)
    
    # remove articles
    name <- gsub("\\b(a|an|the)\\b", "", name, perl = T)
    
    # fix white spaces
    name_ <- str_split(name, "\\s+", simplify = T)
    name <- paste(name_[name_ != ""], collapse = " ")
    return(name)
  }
  
  lines <- readLines(path, ok = T, warn = F)
  
  N <- length(lines)
  
  # dict to map names of predictions to ids
  names_to_id <- list()
  id_to_count <-  list()
  
  for(index in 1:N){
    
    line <- lines[index]
    
    json.data <- fromJSON(line)
    
    objects.uris <- json.data[["obj_uris"]]
    for(i in 1:length(objects.uris)){
        
      uri <- objects.uris[i]
        
      # first time we meet this id ?
        if (! uri %in% names_to_id) {
            
            for (name  in c(json.data[["obj_labels"]][i], unlist(json.data[["obj_aliases"]][i]) )) {
              names_to_id[[name_normalise(name)]] <- uri
            }
            id_to_count[[uri]] <- 1
        }

        # not the first time, increment count
        else{
            id_to_count[[uri]] <- id_to_count[[uri]] + 1
        }
    }
  }
  return(list(names_to_id, id_to_count))
  
}



bias_from_training_dataset <- function(path_to_train, l_train, bif.df, ref, top=5){
  
  prediction_data <- bif.df[bif.df$ref == ref, ]
  prop_stats <- frequency_of_object_in_train_data(path_to_train)
  prop_name_to_id <- prop_stats[[1]]
  prop_id_to_count <- prop_stats[[2]]
  df_prop_id_to_count <- data.frame(object.id = names(prop_id_to_count), count_in_train = as.integer(prop_id_to_count))
  # On fait le top par rapport aux rank et nonpas par les object.ids, comme ça, si jamis plusieurs objets ont la fréquence atteinte au top choisi, alors tous sont gardés.
  temp_df <- data_frame(count_in_train = unique(df_prop_id_to_count$count_in_train))
  temp_df <- temp_df[order(temp_df$count_in_train, decreasing = T), ]
  temp_df$index <- 1:nrow(temp_df)
  temp_df$isintop <- temp_df$index <= top

  df_prop_id_to_count <- df_prop_id_to_count %>% left_join((temp_df %>% select(count_in_train, isintop)), by = "count_in_train")
  
  df_prop_name_to_id <- data.frame(preds.label = names(prop_name_to_id),  object.id = as.character(prop_name_to_id))
 
  prediction_data <- prediction_data %>% left_join(df_prop_name_to_id, by = "preds.label") %>% left_join(df_prop_id_to_count, by = "object.id")
  prediction_data[is.na(prediction_data$isintop), ]$isintop <- FALSE
  
  data_for_plot <- prediction_data %>% group_by(preds.rank, isintop) %>% summarise(n = n())
  data_for_plot <- data_for_plot %>% group_by(preds.rank) %>% mutate(prop = (n/sum(n)) * 100)
  
  p <- data_for_plot %>% ggplot(aes(x = preds.rank, y = prop, fill = isintop)) +
  geom_bar(stat="identity") +
  theme_classic() +
  scale_fill_discrete(drop=FALSE) +
  theme(axis.text = element_text(size = 20), text = element_text(size = 15)) +
  xlab("") + 
  ylab("")
  # ggtitle(paste("property= ", ref))
  return(list(prediction_data, p))
}


compute_pred_LCP <- function(x, y) {
    # Remove punctation or digit characters (if chemical for instance):
    process_str <- function(x) {
      tolower(gsub('[[:punct:][:digit:]]+','',x))
    }
    x.processed <- process_str(x)
    y.processed <- sapply(y, FUN = process_str, simplify = T, USE.NAMES = F)
    
    longest <- 0
    # cut x by space
    for (ind.x in strsplit(x.processed, " ")[[1]]) {
      # print(ind.x)
      # also test on all y cuted by space
      for(ind.y in strsplit(y.processed, " ")[[1]]){
        # test if longest prefix is
        l <- nchar(longestCommonPrefix(c(ind.x, ind.y)))
        if(l > longest){
          longest <- l
        }
      }
    }
    return(longest)
  }


LCP_permutation_test <- function(preds, subject2labels, nsims){
  
  out <- data.frame()
  
  preds <- preds %>% mutate(prop = str_split(ref, "-", simplify = T)[, 1])
  seeds <- unique(preds$seed)
  refs <- unique(preds$ref)
  
  for(r in refs){
    
    print(paste("Ref: ", r))
    
    for(s in seeds){
      
      nge <- 0
      
      print(paste("Seed", s))
      
      # Déjà, on ne récupère que les predictions correctes:
      correct.preds <- preds %>% filter(is.correct, ref == r, seed == s)
      # On met les labels:
      correct.preds <- correct.preds %>% left_join((subject2labels %>% select(subject.id, subject.label, prop)), by = c("subject.id", "prop"))
      
      correct.preds <- correct.preds %>% select(subject.label, preds.label)
      
      LCPs <- apply(correct.preds, 1, FUN = function(x){LCP(x[1], x[2])})
      AVG.LCP <- mean(LCPs)
      MED.LCP <- median(LCPs)
      MIN.LCP <- min(LCPs)
      MAX.LCP <- max(LCPs)
      
      for(i in 1:nsims){
        # print(paste("sim: ", i))
        correct.preds$subject.label <- sample(correct.preds$subject.label)
        correct.preds$preds.label <- sample(correct.preds$preds.label)
        avg.sim.LCP <- mean(apply(correct.preds, 1, FUN = function(x){LCP(x[1], x[2])}))
        if(avg.sim.LCP > AVG.LCP){
          nge <- nge + 1
        }
      
      }
      p.v.monte.c <- (nge + 1) / (nsims + 1)
      tmp <- data.frame("ref" = r, "seed" = s, "AVG.LCP" = AVG.LCP, "MED.LCP" = MED.LCP, "MIN.LCP" = MIN.LCP, "MAX.LCP" = MAX.LCP, "est.p.v" = p.v.monte.c)
      out <- rbind(out, tmp)
    }
  }
  return(out)
}


get_table_labels <- function(path){
  
  lines <- readLines(path, ok = T, warn = F)
  
  N <- length(lines)
  
  out <- data.frame("subject.id" = vector("character", N), "subject.label" = vector("character", N))

  for(index in 1:N){
    
    line <- lines[index]
    
    json.data <- fromJSON(line)
    
    subject.id <- json.data[["sub_uri"]]
    
    # On ne considère pas les synonymes car ils ne sont pas envoyé au modèle.
    subject.label <- json.data[["sub_label"]]
    
        
    out[index, "subject.id"] <- subject.id
    out[index, "subject.label"] <- subject.label
  }
  return(out)
}

```


# Best manual-prompting results
```{r}

manual_model_ref <- c("P703-manual*", "rP703-manual*")

manual_model_res <- c("../Exp-Taxa-NP-ANALYSES/output/np/manual/PubMedBERT/manual2/confidence/none/P703.json",
               "../Exp-Taxa-NP-ANALYSES/output/np/manual/PubMedBERT-full/manual1/order/confidence/rP703.json")

manual_model_res_masked <- c("../Exp-Taxa-NP-ANALYSES/output/np/manual/PubMedBERT/manual2/confidence/none/MASKED/P703.json",
                      "../Exp-Taxa-NP-ANALYSES/output/np/manual/PubMedBERT-full/manual1/order/confidence/MASKED/rP703.json")


list.of.df <- list()

for(index in 1:2){
  
  print("<=====================")
  print(manual_model_ref[index])
  p1 <- manual_model_res[index]
  p2 <- manual_model_res_masked[index]
  
  print(paste("- Std. file at: ", p1))
  print(paste("- Masked. file at: ", p2))
  
  std <- extract_prediction_proba_pairs(read_predictions(p1)) %>% distinct()
  masked <- extract_prediction_proba_pairs(read_predictions(p2)) %>% distinct()
  
  masked_for_merging <- (masked %>% select(preds.label, preds.rank))
  colnames(masked_for_merging) <- c("preds.label", "rank.in.masked")
  
  comp <- std %>% left_join(masked_for_merging, by = "preds.label")
  comp[is.na(comp$rank.in.masked), ]$rank.in.masked <- -1
  
  # comp <- compare_std_exp_to_masked(std, masked)
  
  # fill with metadata
  comp$ref <- manual_model_ref[index]
  
  list.of.df[[index]] <- comp
  
  print("=====================>")
  
  index <- index + 1
}
          
manual_big.df <- do.call("rbind", list.of.df)

# remove null predictions (== "") or prediction that are just a number.
manual_big.df <- manual_big.df[ (manual_big.df$preds.label != "") , ]
```



# get results for opti-best model

```{r}

opti_model_ref <- c("P703-opti*", "rP703-opti*")

opti_model_prop <- c("P703.json", "rP703.json")

# opti_model_res_dir <- c("../Exp-Taxa-NP-ANALYSES/output/np/opti/PubMedBERT-full/manual1/order/none", "../Exp-Taxa-NP-ANALYSES/output/np/opti/PubMedBERT-full/FS/order/confidence")
opti_model_res_dir <- c("../Exp-Taxa-NP-ANALYSES/output/np/opti2/PubMedBERT/manual1/confidence/none", "../Exp-Taxa-NP-ANALYSES/output/np/opti2/PubMedBERT-full/manual1/order/confidence")

# seeds <- c("seed0", "seed64")
seeds <- c("seed0", "seed64", "seed333", "seed566", "seed999")
```




```{r}

j <- 1

list.of.df <- list()

for(index in 1:2){
  
  for(seed in seeds){

    print("<=====================")
    print(opti_model_ref[index])
    p1 <- paste(c(opti_model_res_dir[index], seed, opti_model_prop[index]), collapse = '/')
    p2 <- paste(c(opti_model_res_dir[index], seed, "MASKED", opti_model_prop[index]), collapse = '/')
    
    print(paste("- Std. file at: ", p1))
    print(paste("- Masked. file at: ", p2))
    
    std <- extract_prediction_proba_pairs(read_predictions(p1)) %>% distinct()
    masked <- extract_prediction_proba_pairs(read_predictions(p2)) %>% distinct()
    
    masked_for_merging <- (masked %>% select(preds.label, preds.rank))
    colnames(masked_for_merging) <- c("preds.label", "rank.in.masked")
    
    comp <- std %>% left_join(masked_for_merging, by = "preds.label")
    comp[is.na(comp$rank.in.masked), ]$rank.in.masked <- -1
    
    # comp <- compare_std_exp_to_masked(std, masked)
    
    # fill with metadata
    comp$ref <- opti_model_ref[index]
    comp$seed <- seed
    
    list.of.df[[j]] <- comp
    
    print("=====================>")
    
    j <- j + 1
  }
}
          
opti_big.df <- do.call("rbind", list.of.df)

# remove null predictions (== "") or prediction that are just a number.
opti_big.df <- opti_big.df[ (opti_big.df$preds.label != "") , ]

```


```{r}
p1 <- create_plot(manual_big.df, "P703-manual*")
p2 <- create_plot(manual_big.df, "rP703-manual*")
p3 <- create_plot(opti_big.df, "P703-opti*")
p4 <- create_plot(opti_big.df, "rP703-opti*")

```

```{r}

p2 <- p2 + xlab("Prediction ranks")
p4 <- p4 + xlab("Prediction ranks")

p1 <- p1 + ylab("Proportion of predictions")
p2 <- p2 + ylab("Proportion of predictions")

full <- ggarrange(p1, p3, p2, p4, 
                  labels = c("A", "B", "C", "D"),
                  font.label = list(size = 20, color = "black", face = "bold", family = NULL), 
                  common.legend = T, 
                  legend = "right", ncol = 2, nrow = 2)

```

```{r}
plot(full)
```



* * *

# On calcule les Acc par rapport au leakge.

```{r}
test_data <- c("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/P703/test.jsonl", "../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/rP703/test.jsonl")
```


# get the leakage data
```{r}
# limite de la taille du prefixed commun
LCP_limit <- 5
test_data_P703 <- read_test_data(test_data[1])
test_data_P703$prop <- "P703"

test_data_rP703 <- read_test_data(test_data[2])
test_data_rP703$prop <- "rP703"

LCP_for_join <- rbind((test_data_P703 %>% select(subject.id, prop, LCP)), (test_data_rP703 %>% select(subject.id, prop, LCP)))
```

pour la taille des samples:
```{r}
LCP_for_join %>% group_by(prop) %>% summarise(size.leakage.set = n_distinct(subject.id[LCP >= LCP_limit]), size.not.leakage.set = n_distinct(subject.id) - n_distinct(subject.id[LCP >= LCP_limit]) )
```

- for opti.
```{r}
opti_big.df %>% mutate(prop = str_split(ref, "-", simplify = T)[, 1]) %>% 
  left_join(LCP_for_join, by = c("prop", "subject.id")) %>% 
  mutate(ObjectLeaked = LCP >= 2) %>% 
  group_by(ref, ObjectLeaked, seed) %>%
  summarise(Acc5 = signif((n_distinct(subject.id[is.correct==T & preds.rank <= 5]) / n_distinct(subject.id)) * 100, 2)) %>%
  group_by(ref, ObjectLeaked) %>%
  summarise("Avg.acc@5" = mean(Acc5)) %>%
  DT::datatable()
```

- for manual
```{r}

opti_big.df %>% filter(is.correct) %>% mutate(prop = str_split(ref, "-", simplify = T)[, 1]) %>% 
  left_join(LCP_for_join, by = c("prop", "subject.id"))
```

## AVEC le test de permutation.

```{r}
labels_P703 <- get_table_labels(test_data[1])
labels_P703$prop <- "P703"
labels_rP703 <- get_table_labels(test_data[2])
labels_rP703$prop <- "rP703"

subject2labels <- rbind(labels_P703, labels_rP703)

cc <- LCP_permutation_test(opti_big.df, subject2labels)
```


* * *
For manual:
```{r}
manual_preds_frequency <- manual_big.df %>% group_by(ref, preds.label) %>% summarise(n = n_distinct(subject.id))
manual_preds_frequency <- manual_preds_frequency %>% left_join((manual_big.df %>% group_by(ref) %>% summarise(N = n_distinct(subject.id))), by = "ref")
manual_preds_frequency$freq <- (manual_preds_frequency$n / manual_preds_frequency$N) * 100

manual_correcte_preds_and_freq <- manual_big.df %>% filter(is.correct) %>% left_join((manual_preds_frequency %>% select(-c(n, N))), by = c("ref", "preds.label"))

manual_correcte_preds_and_freq %>% group_by(ref) %>% summarise(median = median(freq),
                                                        min = min(freq),
                                                        max = max(freq))

```


For opti
```{r}

opti_preds_frequency <- opti_big.df %>% group_by(ref, preds.label, seed) %>% summarise(n = n_distinct(subject.id))
opti_preds_frequency <- opti_preds_frequency %>% left_join((opti_big.df %>% group_by(ref, seed) %>% summarise(N = n_distinct(subject.id))), by = "ref")
opti_preds_frequency$freq <- (opti_preds_frequency$n / opti_preds_frequency$N) * 100

opti_preds_frequency <- opti_preds_frequency %>% group_by(ref, preds.label) %>% summarise(freq = mean(freq))

opti_correcte_preds_and_freq <- opti_big.df %>% filter(is.correct) %>% left_join(opti_preds_frequency, by = c("ref", "preds.label"))

opti_correcte_preds_and_freq %>% group_by(ref) %>% summarise(median = median(freq),
                                                        min = min(freq),
                                                        max = max(freq))


```



Et si on essayais de savoir si les predictions correctes était soient des trucs fréquent et/ou juste du LCP

```{r}
labels_P703 <- get_table_labels(test_data[1])
labels_P703$prop <- "P703"
labels_rP703 <- get_table_labels(test_data[2])
labels_rP703$prop <- "rP703"

subject2labels <- rbind(labels_P703, labels_rP703)
```


Pour opti:
```{r}

get_class_of_preds <- function(data, subject2labels, LCP_LIMIT){

data <- data %>% mutate(prop = str_split(ref, "-", simplify = T)[, 1])
data_for_table <- data %>% filter(is.correct) %>% left_join(subject2labels, by = c("subject.id", "prop"))


data_for_table$LCP <- apply((data_for_table %>% select(subject.label, preds.label)), 1, FUN = function(x){compute_pred_LCP(x[1], x[2])})
data_for_table$test_LCP <- as.integer(data_for_table$LCP >= LCP_LIMIT)

top_answers <- rbind( (data %>% filter(is.correct, prop == "P703") %>% group_by(preds.label) %>% summarise(n = n()) %>% slice_max(order_by = n, n = 5)), 
                      (data %>% filter(is.correct, prop == "rP703") %>% group_by(preds.label) %>% summarise(n = n()) %>% slice_max(order_by = n, n = 1)))

print(top_answers)

data_for_table$test_freq <- as.integer(data_for_table$preds.label %in% top_answers$preds.label)

data_for_table <- data_for_table %>% mutate(Class = paste0(test_freq, test_LCP))
data_for_table$Class <- factor(data_for_table$Class, levels = c("00", "10", "01", "11"), labels = c("Original", "Top-Freq", "Leak", "Top-Freq & Leak"))

return(list(data_for_table, (data_for_table %>% group_by(prop, Class) %>% summarise(n = n()) %>% group_by(prop) %>% mutate(p = round(n / sum(n) * 100, 2) ))))

}

LCP_LIMIT <- 5
manual <- get_class_of_preds(manual_big.df, subject2labels, LCP_LIMIT)
opti <- get_class_of_preds(opti_big.df, subject2labels, LCP_LIMIT)

data_for_plot <- rbind( (manual[[2]] %>% mutate(Exp = "Manual*")), (opti[[2]] %>% mutate(Exp = "Opti*")) )
data_for_plot <- data_for_plot %>% mutate(label = paste("(", p, " %)"))

data_for_plot %>% 
  ggplot(aes(x = Exp, y = p, fill = Class, label = label)) + 
  geom_bar(stat = "identity", position = "stack") +
  theme_classic() +
  geom_text(size = 6, position = position_stack(vjust = 0.5)) +
  theme(axis.text = element_text(size = 20, colour="black"), text = element_text(size = 15, colour="black")) +
  facet_grid(. ~ prop) +
    scale_fill_brewer(palette="Set1")

data_for_plot %>% group_by(prop, Exp) %>% summarise(N = sum(n))
```




* * *


```{r}

# tmp1 <- bias_from_training_dataset("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/P703/train.jsonl", 1546, manual_big.df, "P703-manual*")
tmp1 <- bias_from_training_dataset("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/P703/big_train.jsonl", 1933, manual_big.df, "P703-manual*")
d1 <- tmp1[[1]]
p1.2 <- tmp1[[2]]

tmp2 <- bias_from_training_dataset("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/rP703/big_train.jsonl", 500, manual_big.df, "rP703-manual*")
d2<- tmp2[[1]]
p2.2 <- tmp2[[2]]

tmp3 <- bias_from_training_dataset("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/P703/big_train.jsonl", 1933, opti_big.df, "P703-opti*")
d3 <- tmp3[[1]]
p3.2 <- tmp3[[2]]

tmp4 <- bias_from_training_dataset("../Exp-Taxa-NP-ANALYSES/data/np/triples_processed/rP703/big_train.jsonl", 500, opti_big.df, "rP703-opti*")
d4 <- tmp4[[1]]
p4.2 <- tmp4[[2]]

```

```{r}

p2.2 <- p2.2 + xlab("Prediction ranks")
p4.2 <- p4.2 + xlab("Prediction ranks")

p1.2 <- p1.2 + ylab("Proportion of predictions")
p2.2 <- p2.2 + ylab("Proportion of predictions")

full2 <- ggarrange(p1.2, p3.2, p2.2, p4.2, 
                  labels = c("A", "B", "C", "D"),
                  font.label = list(size = 20, color = "black", face = "bold", family = NULL), 
                  common.legend = T, 
                  legend = "right", ncol = 2, nrow = 2)

```

```{r}
plot(full2)
```


J'a aussi exporter les tables ;)
