---
title: "create-tranformers-tuning-dataset"
author: "Maxime Delmas"
date: "2022-11-30"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Requête 1: Extracttion des relations fungi ("species") - PubChen ID avec le nombre de références supportant chacunes de ces associations.
fungi2pubchen.csv

```{sql}
DEFINE input:inference "schema-inference-rules"

select ?fungi_id (STRAFTER(STR(?compound), "http://rdf.ncbi.nlm.nih.gov/pubchem/compound/CID")as ?pubchem_id) ?nb_ref
FROM <https://abroad/mycobank-taxonomy>
FROM <https://abroad/species2pubchem>
FROM <https://abroad/pubchem/compound>
FROM <https://abroad/chebi>
WHERE
{
	{
		SELECT ?assos (count(distinct ?ref) as ?nb_ref)
		WHERE
		{
			?assos sio:SIO_000628 ?fungi, ?compound ;
				sio:SIO_000253 ?ref	
			
		}
		GROUP BY ?assos
	}
	?assos sio:SIO_000628 ?fungi, ?compound .

	?fungi a dwc:Taxon ;
		dwc:taxonRank "species" ;
		dwc:taxonID ?fungi_id .

	?compound a chebi:23367 .
}
```

## Reauête 2: Extraire les noms, et noms des familles des composés
ATTENTION: CERTAIN PEUVENT ETRE DES SYN
-file: fungi_nomenclature.csv
(Plus facile sans inférence pour la transitivité)
```{sql}
select distinct ?fungi_id ?fungi_name ?family_name
FROM <https://abroad/mycobank-taxonomy>
WHERE
{
	?fungi dwc:taxonRank "species" ;
		dwc:taxonID ?fungi_id ;
		rdfs:label ?fungi_name .

?fungi abroad:isSynonymTaxonOf/abroad:isChildTaxonOf+|abroad:isChildTaxonOf+ ?ancestor .

	?ancestor dwc:taxonRank "family" ;
		rdfs:label ?family_name .
}

```

## Requête 3: Extraction de tous les conposés produit par des fungi ("species") ainsi aue leur activité antibio (0/1)
-file: compound_activity.csv
```{sql}

DEFINE input:inference "schema-inference-rules"

select distinct (STRAFTER(STR(?compound), "http://rdf.ncbi.nlm.nih.gov/pubchem/compound/CID")as ?pubchem_id)  ?y
FROM <https://abroad/chebi>
FROM <https://abroad/mycobank-taxonomy>
FROM <https://abroad/species2pubchem>
FROM <https://abroad/pubchem/compound>
where
{
?fungi a dwc:Taxon ;
	dwc:taxonRank "species" ;
	abroad:taxonProduces ?compound .

?compound rdf:type ?chebi .

?chebi rdfs:subClassOf [ a owl:Restriction ;
		owl:onProperty obo:RO_0000087 ;
		owl:someValuesFrom ?role ] ;
	
	<http://www.geneontology.org/formats/oboInOwl#inSubset> <http://purl.obolibrary.org/obo/chebi#3_STAR>
	
BIND ( exists{ ?role rdfs:subClassOf* chebi:33281 } AS ?y)
}

```

Requête 4: list of all compounds:
`
```{sql}

DEFINE input:inference "schema-inference-rules"

select distinct (STRAFTER(STR(?compound), "http://rdf.ncbi.nlm.nih.gov/pubchem/compound/CID")as ?pubchem_id)
FROM <https://abroad/mycobank-taxonomy>
FROM <https://abroad/species2pubchem>
FROM <https://abroad/pubchem/compound>
where
{
?fungi a dwc:Taxon ;
	dwc:taxonRank "species" ;
	abroad:taxonProduces ?compound .
}
```

### Creating the dataset

1) get fungi - compound associations
```{r}

# data for fungi - pubchem
fungi_pubchem <- read_csv("data/fungi2pubchen.csv")

# Some fungi don't have annotated family or genus, so we need to check on that first.
nomenclature_data <- read_csv("data/fungi_nomenclature.csv")

# keep fungi for which precise taxonomic info is available.
fungi_pubchem <- fungi_pubchem %>% left_join(nomenclature_data, by = 'fungi_id')
fungi_pubchem <- fungi_pubchem[! is.na(fungi_pubchem$family_name), ]

# data for pubchem to antibioactivity
pubchem_antibio_activity <- read_csv("data/compound_activity.csv")

# Warning: if a compound has differents roles it may have a line yith no activity and an other with activity, so fusion by summing to see if it has at least one activity
pubchem_antibio_activity <- pubchem_antibio_activity %>% group_by(pubchem_id) %>% summarise(y = sum(y))

# merge
fungi_pubchem <- fungi_pubchem %>% left_join(pubchem_antibio_activity, by='pubchem_id')

# for compounds we don't have information on roles from chebi, set y = -1
fungi_pubchem[is.na(fungi_pubchem$y), ]$y <- -1

```


# Extract the first part of the "producing-positive" set: Fungi produce chemical with antibiotic activities
```{r}

# extract positives triplets: fungi - pubchem - antibioactiviy
positives_fungi_pubchem <- fungi_pubchem[(fungi_pubchem$y == 1), ]

# order by nb_ref
positives_fungi_pubchem <- positives_fungi_pubchem[order(positives_fungi_pubchem$nb_ref, decreasing = T), ]

# add number of distinct fungi on table ordered by decreaing nb_ref:
v_Fungi_set_size <- vector(mode="numeric", length = nrow(positives_fungi_pubchem))
for(i in 1:nrow(positives_fungi_pubchem)) {
    v_Fungi_set_size[i] <- length(unique(positives_fungi_pubchem[1:i, ]$fungi_id))
}
positives_fungi_pubchem$Fungi_set_size <- v_Fungi_set_size


# extract data until have n differents species:
n <- 100
min_index <- max(which(positives_fungi_pubchem$Fungi_set_size == n))
selected_postives_rows_fungi_pubchem <- positives_fungi_pubchem[1:min_index, ]
```


# Extract the second part of the "producing-positive" set: Fungi produce chemical with NO antibiotic activities

```{r}

# get the list of the 100 fungi previously extracted
fungi_list <- unique(selected_postives_rows_fungi_pubchem$fungi_id)

# extract negative triplets: fungi produce - NO antibiotic activity
negatives_fungi_pubchem <- fungi_pubchem[(fungi_pubchem$y == 0), ]
negatives_fungi_pubchem <- negatives_fungi_pubchem[order(negatives_fungi_pubchem$nb_ref, decreasing = T), ]

# keep only lines involving the selected list of fungi
negatives_fungi_pubchem <- negatives_fungi_pubchem[negatives_fungi_pubchem$fungi_id %in% fungi_list, ]

# Extract the same number of lines as in the positives
selected_negatives_rows_fungi_pubchem <- negatives_fungi_pubchem[1:nrow(selected_postives_rows_fungi_pubchem), ]
```

## merge the both 

```{r}

dataset_fungi_produce <- rbind((selected_postives_rows_fungi_pubchem %>% select(-Fungi_set_size)), selected_negatives_rows_fungi_pubchem)

```

Attention, comme on a sélectionné les composés depuis les positive, il n'est pas garanti que les n champignons du set positif (produisant un cpd avec antibio act.) soit référencés comme produisant un composé qui n'a pas d'activité... Donc certains Fungi peuvent être unique au set: Fungi-produce-chemWithAct

### First balance checking

```{r}
data_dist_fungi_in_dataset <- dataset_fungi_produce %>% group_by(fungi_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset$n), 1))
```


```{r}
data_dist_fungi_in_dataset2 <- dataset_fungi_produce %>% group_by(pubchem_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset2, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset2$n), 1))
```

La distribution semble OK !


2) Preparing negatives pairs:

On cherche deja à récupéré toutes les paires connues d'un Fungi qui produirait un composé.
En connaissant la famille du Fungi, cela nous permet de créer des paires Fungi-family - produce Chem

```{r}
# Create a table: "Family X is able to produce compound Y which has antibio activity"
families_pubchem_antibiotic_act <- fungi_pubchem %>% select(family_name, pubchem_id, y) %>% distinct() %>% mutate(ID = paste0(family_name, pubchem_id))
```

# Create possibles negatives pairs:


### Première partie du dataset: ne produit pas & act anti
```{r}
# Create all combinations
all_cbn_pos <- expand.grid(unique(selected_postives_rows_fungi_pubchem$fungi_id), unique(selected_postives_rows_fungi_pubchem$pubchem_id))
colnames(all_cbn_pos) <- c("fungi_id", "pubchem_id")

# add family informations of combinations and remove duplicates
all_cbn_pos <- all_cbn_pos %>% left_join((selected_postives_rows_fungi_pubchem %>% select(fungi_id, fungi_name, family_name) %>% distinct()), by = 'fungi_id') %>% mutate(ID = paste0(family_name, pubchem_id))

# remove combibations where the family is already knowm to produce the compound.
all_cbn_pos <- all_cbn_pos[! all_cbn_pos$ID %in% families_pubchem_antibiotic_act$ID, ]

# on selectionne random autant de negative pairs aue de positives
sampled_all_cbn_pos <- all_cbn_pos %>% sample_n(nrow(selected_postives_rows_fungi_pubchem))
sampled_all_cbn_pos$y <- 1
sampled_all_cbn_pos$nb_ref <- -1
```



### seconde partie du dataset: ne produit pas & NO act anti
```{r}
# Create all combinations
all_cbn_neg <- expand.grid(unique(selected_negatives_rows_fungi_pubchem$fungi_id), unique(selected_negatives_rows_fungi_pubchem$pubchem_id))
colnames(all_cbn_neg) <- c("fungi_id", "pubchem_id")

# add family informations of combinations and remove duplicates
all_cbn_neg <- all_cbn_neg %>% left_join((selected_negatives_rows_fungi_pubchem %>% select(fungi_id, fungi_name, family_name) %>% distinct()), by = 'fungi_id') %>% mutate(ID = paste0(family_name, pubchem_id))

# remove combibations where the family is already knowm to produce the compound.
all_cbn_neg <- all_cbn_neg[! all_cbn_neg$ID %in% families_pubchem_antibiotic_act$ID, ]

# on selectionne random autant de negative pairs aue de positives
sampled_all_cbn_neg <- all_cbn_neg %>% sample_n(nrow(selected_postives_rows_fungi_pubchem))
sampled_all_cbn_neg$y <- 0
sampled_all_cbn_neg$nb_ref <- -1
```


## merge the both 

```{r}
dataset_fungi_not_produce <- rbind((sampled_all_cbn_pos %>% select(fungi_id, pubchem_id, nb_ref, fungi_name, family_name, y)), (sampled_all_cbn_neg %>% select(fungi_id, pubchem_id, nb_ref, fungi_name, family_name, y)))
```


### Second balance checking
```{r}
data_dist_fungi_in_dataset <- dataset_fungi_not_produce %>% group_by(fungi_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset$n), 1))
```


```{r}
data_dist_fungi_in_dataset2 <- dataset_fungi_not_produce %>% group_by(pubchem_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset2, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset2$n), 1))
```
# FINAL dataset

```{r}
dataset <- rbind(dataset_fungi_produce, dataset_fungi_not_produce)
```



### Second balance checking
```{r}
data_dist_fungi_in_dataset <- dataset[dataset$nb_ref == -1, ] %>% group_by(fungi_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset$n), 1))
```


```{r}
data_dist_fungi_in_dataset2 <- dataset[dataset$nb_ref == -1, ]  %>% group_by(pubchem_id) %>% summarise(n = n())
ggplot(data_dist_fungi_in_dataset2, aes(x = n)) + geom_histogram(binwidth = 1) + theme_classic() + scale_x_continuous(breaks = seq(1, max(data_dist_fungi_in_dataset2$n), 1))
```


# add chenmical nane

```{r}
chem_name <- read_tsv("data/pubchem_names.tsv", col_names = c("pubchem_id", "chem_name"))
dataset <- dataset %>% left_join(chem_name, by = 'pubchem_id')

write.table(dataset %>% select(fungi_id, fungi_name, family_name, pubchem_id, chem_name, nb_ref, y), sep = '\t', file = "data/dataset.tsv", row.names = FALSE)
```

## test prompt bias

```{r}
# re-read dataset
d <- read_tsv("~/Documents/ABRoad/data/dataset-Tranformers-tuning/data/dataset.tsv")

# Count numner of different families by compounds and producing status and family naée
test <- d %>% mutate(produce = nb_ref > 0) %>% group_by(pubchem_id, produce, family_name) %>% summarise(n = n())

# keep only compounds with at least two distinct fungi associated for the "produce" nor "not-produce" examples
test <- test %>% group_by(pubchem_id, produce) %>% mutate(l = sum(n)) %>% filter(l > 1)

# Calcul des proba de chaque familles pour les champignons associés au composé
test <- test %>% mutate(p = n / l)

# Calcul de l'entropie. On souhaite savoir si l'incertitude relative à la famille derrière un fungi associé à un cpd est inférieure dans les exemples positifs (on suppose que globalement, ils sont souvent de la même famille) par rapport aux exemples négatifs (où l'on s'attend à plus de var.)
test <- test %>% group_by(pubchem_id, produce) %>% summarise(E = -sum((p * log2(p))))

ggplot(test, aes(x = produce, y = E)) + geom_boxplot()



```

Si 










