---
title: "Prompting"
author: "Maxime Delmas"
date: "2023-01-27"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(DT)
```


# Task 2: Chemical [X] has antibiotic activity ?

List of templates:

- Among isolated chemical compounds, {compound} presented {mask} antimicrobial activities.
- Compound {compound} showed {mask} growth inhibition on strains.
- {compound} showed {mask} growth inhibition on strains.
- Compound {compound} showed {mask} growth inhibition on drug-resistant pathogenic strains.
- {compound} showed {mask} growth inhibition on drug-resistant pathogenic strains.
- Compound {compound} {mask} the growth of the strains.
- {compound} {mask} the growth of the strains.
- Compound {compound} is produced by fungus {fungi}. It is {mask}.

## Load results
```{r}
data_JS_divergences <- read_tsv("data/JS_divergence_table_complete_task2_5000.tsv")

longer_data_JS_divergences <- data_JS_divergences %>% pivot_longer(cols = c("PosxPos", "NegxNeg", "PosxNeg"), names_to = "Type", values_to = "JSD")

# remove lines with na in cases of compution errors (i can happen on some lines ...)
longer_data_JS_divergences <- longer_data_JS_divergences[! is.na(longer_data_JS_divergences$JSD), ]

# laod top 20
top_20 <- read_tsv("data/top_k_table_task2.tsv")
top_20$Template <- as.factor(top_20$Template)
top_20$model <- as.factor(top_20$model)
top_20$Type <- as.factor(top_20$Type)



top1_cor <- read_tsv("data/top_1_cor_task2.tsv")
# top1_cor <- top1_cor %>% pivot_wider(names_from = Template, values_from = cors)
```

## 1 - Compare distribution of JS-duvergences with Kruskal-Wallis chi-squared
```{r}
# See: The need to report effect size estimates revisited. An overview of some recommended measures of effect size

# The interpretation values commonly in published literature are: 0.01- < 0.06 (small effect), 0.06 - < 0.14 (moderate effect) and >= 0.14 (large effect).

# -> The KS stats may very a bit from different sampling, but if we look at the boxplot betwwen different samples, mediam, mean, min, etc... are globally thr sane, so its justs the ranks that can be a bit differents, but whatever the conclusions are the same.

# prepare data
KW_data <- longer_data_JS_divergences %>% select(model, Template) %>% distinct()
KW_data$KW_stats <- 0
KW_data$p.value <- 0
KW_data$effect.size <- 0

k <- length(unique(longer_data_JS_divergences$Type))

for (i in 1:nrow(KW_data)) {
  model <- KW_data[i, ]$model
  template <- KW_data[i, ]$Template
  data_kw <- longer_data_JS_divergences[longer_data_JS_divergences$model == model & longer_data_JS_divergences$Template == template, ]
  n <- nrow(data_kw)
  kw <- kruskal.test(JSD ~ Type, data = data_kw)
  KW_data[i, ]$KW_stats <- as.numeric(kw$statistic)
  KW_data[i, ]$p.value <- as.numeric(kw$p.value)
  KW_data[i, ]$effect.size <- (as.numeric(kw$statistic) - k + 1) / (n - k) * 100
}

DT::datatable(KW_data)
```

While most of the comparison are signficant due to sample size, we can clearly see that the effect size indicate a small amount of variance explained by the Type of the comparison: PosxPos, NegxNeg or PosxNeg.

La taille d'effet maximale observé est autour de 2.46%, ce qui est très faible.


# Produce graph by template
```{r, fig1, out.width="100%", fig.width = 8, fig.height = 6, message=FALSE}
for(template in unique(longer_data_JS_divergences$Template)){
  g <- longer_data_JS_divergences %>% filter(Template == template) %>% ggplot(aes(x = Type, y = JSD)) +
    geom_boxplot() +
    theme_classic() +
    facet_wrap(. ~ model) +
    ggtitle(paste("Template: ", template))
  plot(g)
}
```


# Compute with proportion test

## Comptue proportion test: 

By re-sampling 5000 JS-divergence fron the different set, estimate:
  - the proportion of PosxNeg > NegxNeg
  - the proportion of PosxNeg > PosxPos

Simply 
```{r}

n <- 5000

prop_data_computation <- longer_data_JS_divergences %>% select(model, Template) %>% distinct()
prop_data_computation$vs_Neg <- 0
prop_data_computation$vs_Pos <- 0

for (i in 1:nrow(prop_data_computation)) {
  
  model <- prop_data_computation[i, ]$model
  template <- prop_data_computation[i, ]$Template
  
  # Compare PosxNeg to Posxpos:
  PosxNeg <- sample(longer_data_JS_divergences[longer_data_JS_divergences$model == model & longer_data_JS_divergences$Template == template & longer_data_JS_divergences$Type == "PosxNeg", ]$JSD, replace = T, size = n)
  NegxNeg <- sample(longer_data_JS_divergences[longer_data_JS_divergences$model == model & longer_data_JS_divergences$Template == template & longer_data_JS_divergences$Type == "NegxNeg", ]$JSD, replace = T, size = n)
  PosxPos <- sample(longer_data_JS_divergences[longer_data_JS_divergences$model == model & longer_data_JS_divergences$Template == template & longer_data_JS_divergences$Type == "PosxPos", ]$JSD, replace = T, size = n)
  
  prop_data_computation[i, ]$vs_Neg <- ( sum(PosxNeg > NegxNeg) / n )
  prop_data_computation[i, ]$vs_Pos <- ( sum(PosxNeg > PosxPos) / n )
}
```

## Plot heatmaps


### Compare with PosxPos

```{r}
# Give extreme colors:
ggplot(prop_data_computation, aes(model, factor(Template), fill = vs_Neg)) + 
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  geom_text(aes(label = vs_Neg), color = "white", size = 4) +
  scale_fill_gradient2(low = "#075AFF",
                       mid = "#FFFFCC",
                       high = "#FF0000",
                       limits = c(0,1)) +
  coord_fixed() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

### Compare with PosxPos
```{r}
# Give extreme colors:
ggplot(prop_data_computation, aes(model, factor(Template), fill = vs_Pos)) + 
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  geom_text(aes(label = vs_Pos), color = "white", size = 4) +
  scale_fill_gradient2(low = "#075AFF",
                       mid = "#FFFFCC",
                       high = "#FF0000",
                       limits = c(0,1)) +
  coord_fixed() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


In the both cases we see that pour toutes les combinaison de Template x Model, la proportion de fois ou la divergence obtenue en comparant positif vs négatifs à des paires issues du même set n'est jamais supérieure à 0.6.

On a donc pareil une très faible taille d'effet.

## Top 20 tokens

```{r}
DT::datatable(top_20, filter = 'top')

```

## Top 1 cor

```{r}
# Give extreme colors:
ggplot(top1_cor, aes(model, factor(Template), fill = cors)) + 
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  geom_text(aes(label = round(cors, 2)), color = "white", size = 4) +
  scale_fill_gradient2(low = "#075AFF",
                       mid = "#FFFFCC",
                       high = "#FF0000",
                       limits = c(0,1)) +
  coord_fixed() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


Donc pareil au niveau de la corrélation entre les top 1 token prédits.

